**The Place of Interoception and Theory of Mind in Deception**

### 2021-11-24 3_ToM.Rmd
add stars

  annot <- results$marginal_effects  
  annot$Label <- insight::format_p(annot$p, stars_only = TRUE)
  annot$x <- mean(range(data[[var]]))
  annot$x <- ifelse(annot$Condition == "Polygraph", 
                    annot$x - 0.05 * range_x, 
                    annot$x + 0.05 * range_x)
  annot$y <- max(data[[outcome]]) - 0.01 * diff(range(data[[outcome]]))

@@

p_conf_yoni_total <- plot_effect(model, results, var = "YONI_Total", outcome = "Confidence")
# p_conf_yoni_total
```

>>>>

  annot <- results$marginal_effects  
  annot$Label <- insight::format_p(annot$p, stars_only = TRUE)
  annot$x <- mean(range(data[[var]]))
  annot$x <- ifelse(annot$Condition == "Polygraph", 
                    annot$x - 0.05 * range_x, 
                    annot$x + 0.05 * range_x)
  annot$y <- max(data[[outcome]], na.rm=TRUE) - 0.01 * diff(range(data[[outcome]], na.rm=TRUE))

@@

p_conf_yoni_total <- plot_effect(model, results, var = "YONI_Total", outcome = "Confidence")
```

### 2021-11-24 4_Intero.Rmd
add stars

```{r message=FALSE, warning=FALSE, fig.height=figheight*4, fig.width=figwidth*1.5}
p_conf_maia_total / 
  p_conf_maia_noticing / 
  p_conf_maia_notdistracting / 
  p_conf_maia_bodylistening /
  p_conf_maia_trusting / 
  p_conf_maia_notworrying / 
  p_conf_maia_emotionalawareness / 
  p_conf_maia_attentionregulation / 
  p_conf_maia_selfregulation +
  patchwork::plot_annotation(title = "Interoception (MAIA)", theme = theme(plot.title = element_text(hjust = 0.5)))

p_rt_maia_total / 
  p_rt_maia_noticing / 
  p_rt_maia_notdistracting / 
  p_rt_maia_bodylistening /
  p_rt_maia_trusting / 
  p_rt_maia_notworrying / 
  p_rt_maia_emotionalawareness / 
  p_rt_maia_attentionregulation / 
  p_rt_maia_selfregulation +
  patchwork::plot_annotation(title = "Interoception (MAIA)", theme = theme(plot.title = element_text(hjust = 0.5)))

p_hr_maia_total / 
  p_hr_maia_noticing / 
  p_hr_maia_notdistracting / 
  p_hr_maia_bodylistening /
  p_hr_maia_trusting / 
  p_hr_maia_notworrying / 
  p_hr_maia_emotionalawareness / 
  p_hr_maia_attentionregulation / 
  p_hr_maia_selfregulation +
  patchwork::plot_annotation(title = "Interoception (MAIA)", theme = theme(plot.title = element_text(hjust = 0.5)))
```

>>>>

```{r message=FALSE, warning=FALSE, fig.height=figheight*4, fig.width=figwidth*1.5}
p_conf_maia_total / 
  p_conf_maia_noticing / 
  p_conf_maia_notdistracting / 
  p_conf_maia_bodylistening /
  p_conf_maia_trusting +
  patchwork::plot_annotation(title = "Interoception (MAIA) 1/2", theme = theme(plot.title = element_text(hjust = 0.5)))

p_conf_maia_notworrying / 
  p_conf_maia_emotionalawareness / 
  p_conf_maia_attentionregulation / 
  p_conf_maia_selfregulation +
  patchwork::plot_annotation(title = "Interoception (MAIA) 2/2", theme = theme(plot.title = element_text(hjust = 0.5)))

p_rt_maia_total /
  p_rt_maia_noticing / 
  p_rt_maia_notdistracting / 
  p_rt_maia_bodylistening /
  p_rt_maia_trusting +
  patchwork::plot_annotation(title = "Interoception (MAIA) 1/2", theme = theme(plot.title = element_text(hjust = 0.5)))

  p_rt_maia_notworrying + 
  p_rt_maia_emotionalawareness / 
  p_rt_maia_attentionregulation / 
  p_rt_maia_selfregulation +
  patchwork::plot_annotation(title = "Interoception (MAIA) 2/2", theme = theme(plot.title = element_text(hjust = 0.5)))

p_hr_maia_total / 
  p_hr_maia_noticing / 
  p_hr_maia_notdistracting / 
  p_hr_maia_bodylistening /
  p_hr_maia_trusting +
  patchwork::plot_annotation(title = "Interoception (MAIA) 1/2", theme = theme(plot.title = element_text(hjust = 0.5)))

p_hr_maia_notworrying + 
  p_hr_maia_emotionalawareness / 
  p_hr_maia_attentionregulation / 
  p_hr_maia_selfregulation +
  patchwork::plot_annotation(title = "Interoception (MAIA) 2/2", theme = theme(plot.title = element_text(hjust = 0.5)))
```
